Fail Faster

### 2025-03-19 paper/paper.tex
in this case, later should be now

Property-based testing (PBT) is a software testing technique which uses
random test inputs to validate logical specifications. Recent studies on PBT usage~\cite{inpractice} have shown that
practitioners often interleave PBT with their software development process, sometimes
testing their properties every time they save their code. This means that PBT is often run with very short time
budgets---e.g., between 50 milliseconds and 30 seconds---and it is important
that bugs can be found in that time-frame.\iflater
\jwc{phrasing could suggest ``race against time'' aspect.}\hg{Agree, can't see
how to fit this in yet} \jwc{Also think the phrasing should say something like ``the goal is to fail as fast as possible''}\fi

>>>>

Property-based testing (PBT) is a software testing technique which uses
random test inputs to validate logical specifications. Recent studies on PBT usage~\cite{inpractice} have shown that
practitioners often interleave PBT with their software development process, sometimes
testing their properties every time they save their code. This means that PBT is often run with very short time
budgets---e.g., between 50 milliseconds and 30 seconds---and it is important
that bugs can be found in that time-frame.
\jwc{phrasing could suggest ``race against time'' aspect.}\hg{Agree, can't see
how to fit this in yet} \jwc{Also think the phrasing should say something like ``the goal is to fail as fast as possible''}
